Viscous Transport in Eroding Porous Media

### 2019-09-30 docs/transport/erosion_transport.tex
NM

@@

Once~\eqref{eqn:BIE} is solved for the density function $\eeta$, the
Stokeslets $\llambda_\ell$, and the rotlets $\xi_\ell$, the deformation
tensor, pressure, and vorticity at $\xx \in \Omega$ are
\begin{align}
  \label{eqn:deformationDLP} 
  \ssigma(\xx) &= \int_{\bd\Omega} \mathbf{D}_{\ssigma}(\xx,\yy) 
      \eeta(\yy) ds_{\yy} 
  = \frac{1}{2\pi}\int_{\bd\Omega} \left(
    2\frac{\rr \cdot \nn}{\rho^2} \frac{\rr \cdot \eeta}{\rho^2} \II + 
    \frac{\rr \cdot \eeta}{\rho^4} (\nn \otimes \rr + \rr \otimes \nn) 
    \right. \nonumber \\
    & \qquad\qquad\qquad\qquad\qquad\qquad \left.
    +\frac{\rr \cdot \nn}{\rho^4} (\eeta \otimes \rr + \rr \otimes \eeta) - 
    8\frac{(\rr \cdot \nn)(\rr \cdot \eeta)}{\rho^6}(\rr \otimes \rr)
    \right) \, ds_\yy, \\
%
  p(\xx) &= \int_{\bd\Omega} D_{p}(\xx,\yy) 
      \eeta(\yy) ds_{\yy} 
  = -\frac{1}{\pi}\int_{\bd\Omega} \frac{1}{\rho^2}
    \left(I - 2 \frac{\rr \otimes \rr}{\rho^2}\right) \nn \cdot
      \eeta(\yy)\,ds_\yy, \\
%
  \label{eqn:vorticityDLP} 
  \omega(\xx) &= \int_{\bd\Omega} D_{\omega}(\xx,\yy) 
      \eeta(\yy) ds_{\yy} 
  = -\frac{1}{\pi} \int_{\bd\Omega}
    \frac{(\rr \cdot \nn^\perp) + (\rr \cdot \nn)}{\rho^4} 
      (\rr \cdot \eeta) \, ds_\yy,
\end{align}
respectively. We require the deformation tensor of the double-layer potential at
$\xx \in \bd \Omega$.  Since the deformation tensor of the double-layer
potential is discontinuous across $\bd\Omega$, the jump term 
\begin{align}
  \frac{1}{2} \left(\pderiv{\eeta}{\ss} \cdot \ss \right) \left[
    \begin{array}{cc}
      s_x^2 - s_y^2 & 2s_x s_y \\ 2s_x s_y & s_y^2 - s_x^2
    \end{array}
  \right],
  \label{eqn:deformationJump}
\end{align}
must be added to $\ssigma(\xx)$ for $\xx \in \bd\Omega$.  Finally, the
Stokeslets and rotlets do not have any jumps on $\gamma$, so the
deformation tensor, pressure, and vorticity due to the Stokeslets and
rotlets are straightforward to compute~\cite{poz1992}.  Having computed
the deformation tensor on $\gamma$, the shear stress is computed as
defined in equation~\eqref{eqn:shearStress}.

>>>>

\todo[inline]{The above paragraph seems to repeat a lot of what has been mentioned already, but maybe that is okay.}

@@

Once~\eqref{eqn:BIE} is solved for the density function $\eeta$, the
Stokeslets $\llambda_\ell$, and the rotlets $\xi_\ell$, \nick{we are able to compute the deformation tensor, pressure, and vorticity, defined respectively as}
\begin{align}
  \label{eqn:deformationDLP} 
  \ssigma(\xx) &= \int_{\bd\Omega} \mathbf{D}_{\ssigma}(\xx,\yy) 
      \eeta(\yy) ds_{\yy} 
  = \frac{1}{2\pi}\int_{\bd\Omega} \left(
    2\frac{\rr \cdot \nn}{\rho^2} \frac{\rr \cdot \eeta}{\rho^2} \II + 
    \frac{\rr \cdot \eeta}{\rho^4} (\nn \otimes \rr + \rr \otimes \nn) 
    \right. \nonumber \\
    & \qquad\qquad\qquad\qquad\qquad\qquad \left.
    +\frac{\rr \cdot \nn}{\rho^4} (\eeta \otimes \rr + \rr \otimes \eeta) - 
    8\frac{(\rr \cdot \nn)(\rr \cdot \eeta)}{\rho^6}(\rr \otimes \rr)
    \right) \, ds_\yy, \\
%
  p(\xx) &= \int_{\bd\Omega} D_{p}(\xx,\yy) 
      \eeta(\yy) ds_{\yy} 
  = -\frac{1}{\pi}\int_{\bd\Omega} \frac{1}{\rho^2}
    \left(I - 2 \frac{\rr \otimes \rr}{\rho^2}\right) \nn \cdot
      \eeta(\yy)\,ds_\yy, \\
%
  \label{eqn:vorticityDLP} 
  \omega(\xx) &= \int_{\bd\Omega} D_{\omega}(\xx,\yy) 
      \eeta(\yy) ds_{\yy} 
  = -\frac{1}{\pi} \int_{\bd\Omega}
    \frac{(\rr \cdot \nn^\perp) + (\rr \cdot \nn)}{\rho^4} 
      (\rr \cdot \eeta) \, ds_\yy,
\end{align}
\nick{\st{We require the deformation tensor of the double-layer potential at
$\xx \in \bd \Omega$.}}
Since the deformation tensor of the double-layer potential is discontinuous across the boundary $\bd\Omega$, the jump term 
\begin{align}
  \frac{1}{2} \left(\pderiv{\eeta}{\ss} \cdot \ss \right) \left[
    \begin{array}{cc}
      s_x^2 - s_y^2 & 2s_x s_y \\ 2s_x s_y & s_y^2 - s_x^2
    \end{array}
  \right],
  \label{eqn:deformationJump}
\end{align}
must be added to $\ssigma(\xx)$ for $\xx \in \bd\Omega$.  Finally, the
Stokeslets and rotlets \nick{do not exhibit such jumps, and so the associated components of the deformation tensor, pressure, and vorticity} are straightforward to compute~\cite{poz1992}.  Having computed
the deformation tensor on $\gamma$, the shear stress is computed as
defined in equation~\eqref{eqn:shearStress}.
